Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-27 ICML2019/main.tex
fix bug

\noindent \textbf{Differential Privacy.} 
\begin{definition}
\label{def_epsilon_dp}
$\epsilon-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B].
\end{equation*}

@@

\begin{definition}
\label{def_epsilon_delta_dp}
$(\epsilon,\delta)-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta.
\end{equation*} 
\end{definition}

@@

\subsection{Privacy of Exponential Mechanism Family}
\subsubsection{$\expmech{}{}{}{}$ $\epsilon-$Differential Privacy}
Standard exponential mechanism in $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.

>>>>

\noindent \textbf{Differential Privacy.} 
\begin{definition}
\label{def_epsilon_dp}

A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ is $(\epsilon, \delta)-$differential privacy, if for all adjacent
\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subset Range(\mathcal{M})$:
\begin{equation*}
\Pr[\mathcal{M}(\dataobs) \in \mathcal{S}] = e^\epsilon \Pr[\mathcal{M}(\dataobs') \in \mathcal{S}].
\end{equation*}

@@

@@

\subsection{Privacy of Exponential Mechanism Family}
\subsubsection{$\expmech{}{}{}{}$ $\epsilon-$Differential Privacy}
Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.
